Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report

### 2024-08-09 paper.qmd
Updated designs for cor_mats

pilot_cor_mats <- cor_mats(designsG)

@@

```{r}
out_sexspecific_pilot <- sex_specific_models(designsG)
plot_sexspecific_strength_coefs <- out_sexspecific_pilot$plot
dfmodelsummaries <- out_sexspecific_pilot$summaries
```

>>>>

pilot_cor_mats <- cor_mats(designsG2)

@@

```{r}
out_sexspecific_pilot <- sex_specific_models(designsG2)
plot_sexspecific_strength_coefs <- out_sexspecific_pilot$plot
dfmodelsummaries <- out_sexspecific_pilot$summaries
```
